\documentclass{aci}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{lipsum}
\usepackage{hyperref}
\hypersetup{colorlinks=true}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{makecell}
\usetikzlibrary{automata,positioning,arrows}
\usepackage{caption}
\usepackage{changepage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[numbers]{natbib}
% \usepackage[backend=bibtex,sorting=none]{biblatex}
% \addbibresource{./references/paper.bib}
% \addbibresource{./references/unsorted.bib}
% \addbibresource{./references/def_model.bib}
% \addbibresource{./references/comp_etym.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ep}{\varepsilon}
\newcommand{\eps}[1]{{#1}_{\varepsilon}}

\def\typeofarticle{Review} 
\def\currentvolume{2} 
\def\currentissue{1}
\def\currentyear{2022} 
\def\currentmonth{} 
\def\ppages{xx--xx} 
\def\DOI{10.3934/aci.2022xxx} 
\def\Received{26 March 2022} 
\def\Revised{29 March 2022}
\def\Accepted{30 March 2022} 
\def\Published{xx 2022 }


\numberwithin{equation}{section}
\DeclareMathOperator*{\essinf}{ess\,inf}

\usepackage{array}
\newcolumntype{L}{>{\arraybackslash}m{8cm}}

\hyphenpenalty=10000
\usepackage{cite}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Definition modeling: literature review and dataset analysis}

\author{%
    Noah Gardner\affil{1},
    Hafiz Khan\affil{2} 
    and Chih-Cheng Hung\affil{1,}\corrauth
}%

% \shortauthors is used in copyright information in the end of the paper
\shortauthors{the Author(s)}

\address{%
    \addr{\affilnum{1}}{Laboratory of Machine Vision and Security Research, %
        College of Computing and Software Engineering, Kennesaw State %
        University, Marietta GA, USA}%
    \addr{\affilnum{2}}{Laboratory of Ubiquitous Data Mining, %
        College of Computing and Software Engineering, Kennesaw State %
        University, Marietta GA, USA}}
\corraddr{chung1@kennesaw.edu}

\editor{Pasi Fr\"{a}nti}

\begin{abstract}
    Definition modeling, the task of generating a definition for a given term, is a relatively new area of research applied in evaluating word embeddings. Automatic generation of dictionary quality definitions has many applications in natural language processing, such as sentiment analysis, machine translation, and word sense disambiguation. Additionally, definition modeling is also helpful for evaluating the quality of word embeddings. As more research is done in this field, the need for a summary of different applications, approaches, and obstacles grows apparent. This review provides an overview of the current research in definition modeling and a list of future directions and trends.
\end{abstract}
\keywords{definition modeling; definition generation; natural language processing; word embeddings}
\maketitle

\input{sections/introduction}
\input{sections/methodology}
\input{sections/dataset_results}

\FloatBarrier
\input{sections/future}

\FloatBarrier
\section{Conclusions}
The problem of definition modeling is challenging to solve. Specifically, a major challenge is generating definitions for polysemous words. Since the formulation of the task, researchers have been working on various approaches to generate definitions for creating NLP corpora and the evaluation of word embeddings. In this paper, we provide an overview of definition modeling methods and word embeddings applied to the definition modeling task. We share some benchmark datasets and analyses. Our analysis highlights unique points available in each benchmark dataset, including definition statistics, polyseme statistics, and the overlap across all datasets. Finally, we share the collected datasets in a public GitHub repository. \footnote{
\href{https://github.com/DefinitionModeling/DefModelDatasets.jl}
{https://github.com/DefinitionModeling/DefModelDatasets.jl}
}

\section*{Acknowledgments}
We would like to thank the constructive feedback provided by the reviewers.

\section*{Conflict of interest}
All authors declare no conflicts of interest in this paper.

\bibliographystyle{AIMS}
\bibliography{
./references/paper.bib,
./references/unsorted.bib,
./references/def_model.bib,
./references/comp_etym.bib,
}
% \printbibliography
\end{document}
