\documentclass{aims}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{lipsum}
\usepackage{hyperref}
\hypersetup{colorlinks=true}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{tikz}
\usetikzlibrary{automata,positioning,arrows}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[numbers]{natbib}
% \usepackage[backend=bibtex,sorting=none]{biblatex}
% \addbibresource{./references/paper.bib}
% \addbibresource{./references/unsorted.bib}
% \addbibresource{./references/def_model.bib}
% \addbibresource{./references/comp_etym.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ep}{\varepsilon}
\newcommand{\eps}[1]{{#1}_{\varepsilon}}

\def\typeofarticle{Research Article} \def\currentvolume{1} \def\currentissue{1}
\def\currentyear{2021} \def\currentmonth{} \def\ppages{1--30} \def\DOI{to
appear} \def\Received{June 2022} \def\Accepted{July 2022} \def\Published{October
2022 }
\numberwithin{equation}{section}
\DeclareMathOperator*{\essinf}{ess\,inf}

\usepackage{array}
\newcolumntype{L}{>{\arraybackslash}m{8cm}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Survey on Definition Modeling}

\author{%
    Noah Gardner\affil{1},
    Hafiz Khan\affil{2},
    and Chih-Cheng Hung\affil{1}\corrauth
}%

% \shortauthors is used in copyright information in the end of the paper
\shortauthors{the Author(s)}

\address{%
    \addr{\affilnum{1}}{Laboratory of Machine Vision and Security Research, %
        College of Computing and Software Engineering, Kennesaw State %
        University, Marietta GA, USA}%
    \addr{\affilnum{2}}{Laboratory of Ubiquitous Data Mining, %
        College of Computing and Software Engineering, Kennesaw State %
        University, Marietta GA, USA}}
\corraddr{chung1@kennesaw.edu}

\begin{abstract}
    Definition modeling, the task of generating a definition for a given term,
    is a relatively new area of research applied in the evaluation of word
    embeddings that is gathering attention. Automatic generation of dictionary
    quality definitions has many applications in natural language processing,
    such as sentiment analysis, machine translation, and word sense
    disambiguation. Additionally, definition modeling is also useful for
    evaluating the quality of word embeddings. As more research is done in this
    field, the need for a summary of different applications, approaches, and
    obstacles grows apparent. This survey aims to provide an overview of the
    current research in definition modeling, and to provide a list of future
    directions and trends.
\end{abstract}
\keywords{Definition modeling, definition generation, natural language processing, word embeddings}
\maketitle

\input{sections/introduction}
\input{sections/methodology}
\input{sections/dataset_results}
\FloatBarrier
\input{sections/future}

\FloatBarrier
\section{Conclusion}
In this paper, we provide an overview of definition modeling methods 
and word embeddings applied to the definition modeling task. We share
some benchmark datasets and statistics. Finally, we discuss some challenges
when it comes to solving this task. 

\bibliographystyle{AIMS}
\bibliography{
./references/paper.bib,
./references/unsorted.bib,
./references/def_model.bib,
./references/comp_etym.bib,
}
% \printbibliography
\end{document}
