\section{Datasets and Statistics}

\textbf{GCIDE/WordNet:} The GNU Collaborative International Dictionary of
English (GCIDE) is a free dictionary supplemented with some definitions from
WordNet. Available under the GNU General Public License, GCIDE is a useful
corpus for dictionary definitions for general words. This dataset was modified
by Noraset et al. for their original definition model
\cite{noraset_definition_2016}.

\textbf{Oxford Dictionary:} The Oxford Dictionary of English is a free
dictionary of English words and phrases. Collected by
Gadetsky et al., this dataset features contextual
information for each word along with the definition
\cite{gadetsky_conditional_2018}. This dataset is useful for evaluating the
ability of a model to generate definitions for polysemous words.

\textbf{Urban Dictionary:} The Urban Dictionary is a free dictionary of slang
words and phrases where definitions are crowd-sourced by users. Proposed by
Ni et al., the Urban Dictionary dataset is useful for
idioms and rarely-used phrases which are not contained in other dictionary
datasets \cite{ni_learning_2017}.

\textbf{Wikpedia:} The English Wikipedia is a free online encyclopedia. Proposed
by Ishiwatari et al., it combines the useful tasks of
WordNet, Oxford Dictionary, and Urban Dictionary, since it contains descriptions
of many concepts along with context to be used in context-aware models
\cite{ishiwatari_learning_2019}.

\textbf{Wiktionary:} Wiktionary is a free online dictionary from the same 
parent organization as Wikipedia (Wikimedia Foundation). Used by
several researchers, it is useful as it provides a definitions for a large
number of languages. Researchers who wish to use Wiktionary as a dataset for
multi-lingual definition modeling may find this dataset useful. We share statistics
for the English version of Wiktionary, since most definition modeling methods
focus on English.

\begin{table}
    \centering
    \caption{Dataset Statistics.}
    \include{assets/dataset_stats}
    \label{tab:dataset_stats}
\end{table}

\subsection{Statistics}
Statistics of the datasets listed above are shared in Table
\ref{tab:dataset_stats}. Definition and polyseme ratio denotes the ratio of
each to the number of words available to illustrate the prominence of polysemes
in each dataset. Dataset statistics were calculated for the benchmark datasets
WordNet, Urban Dictionary, Oxford Dictionary, and Wikipedia. Additionally, we
share statistics on the raw GCIDE and Wiktionary datasets.
